QALY Comparisons - Energy Crisis Interventions - NoSupport Baseline

### 2023-11-20 minos/outcomes/QALY_comparison.Rmd
Wrote a generic version of the QALY_comparison.Rmd notebook, where key parameters such as baseline and intervention data are set by arguments to the render call in outcomes/Makefile

---
title: "QALY Comparisons - Energy Crisis Interventions - NoSupport Baseline"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

@@

```{r}
QALY_comparison(base = noSupport,
                base.name = 'energyDownliftNoSupport',
                int = support,
                int.name = 'energyDownlift')
```

@@

```{r}
sf12.plots(base = noSupport,
           base.name = 'energyDownliftNoSupport',
           int = support,
           int.name = 'energyDownlift')
```

```{r}
# base <- noSupport
# base.name <- 'energyDownliftNoSupport'
# int <- support
# int.name <- 'energyDownlift'
# 
# combined <- rbind(base, int)
# 
# ## now SF12 plots for comparison
# p1 <- ggplot(combined, aes(x = year, y = SF_12_MCS, group = intervention, colour = intervention, fill = intervention)) +
#   geom_smooth()
# p2 <- ggplot(combined, aes(x = year, y = SF_12_PCS, group = intervention, colour = intervention, fill = intervention)) +
#   geom_smooth()
# 
# print(p1)
# print(p2)
# 
# combined.SF12 <- combined %>%
#   select(run_id, year, intervention, SF_12_MCS, SF_12_PCS) %>%
#   pivot_wider(names_from = 'intervention',
#               values_from = c('SF_12_MCS', 'SF_12_PCS')) %>%
#   mutate(MCS_diff = .data[[paste0('SF_12_MCS_', int.name)]] - .data[[paste0('SF_12_MCS_', base.name)]],
#          PCS_diff = .data[[paste0('SF_12_PCS_', int.name)]] - .data[[paste0('SF_12_PCS_', base.name)]]) %>%
#   select(run_id, year, MCS_diff, PCS_diff)
# 
# p3 <- ggplot(combined.SF12, aes(x = year, y = MCS_diff)) +
#   geom_smooth() +
#   geom_hline(yintercept = 0, linetype = 'dashed') +
#   labs(title = 'Change in SF_12_MCS', subtitle = paste0(int.name, ' vs ', base.name)) +
#   xlab('Year') +
#   ylab('Change in MCS')
# 
# p4 <- ggplot(combined.SF12, aes(x = year, y = PCS_diff)) +
#   geom_smooth() +
#   geom_hline(yintercept = 0, linetype = 'dashed') +
#   labs(title = 'Change in SF_12_PCS', subtitle = paste0(int.name, ' vs ', base.name)) +
#   xlab('Year') +
#   ylab('Change in MCS')
# 
# print(p3)
# print(p4)

@@

```{r}
auc.plots(base = noSupport, 
          base.name = 'NoSupport',
          intervention = support,
          int.name = 'Support')
```

@@

```{r}
cost.per.qaly(base = noSupport,
              base.name = 'energyDownliftNoSupport',
              int = support,
              int.name = 'energyDownlift',
              QALY_value = 60000,  # QALY value == £60,000
              int.label <- 'EPCG')
```

@@

```{r}
ICER(base = noSupport,
     base.name = 'energyDownliftNoSupport',
     int = support,
     int.name = 'energyDownlift',
     QALY_value = 60000,
     int.label = 'EPCG')
```

@@

```{r}
intervention.cost(base = noSupport,
                  base.name = 'energyDownliftNoSupport',
                  int = support,
                  int.name = 'energyDownlift',
                  int.label = 'EPCG')
```

>>>>

---
title: "QALY Comparisons - Energy Crisis Interventions - NoSupport Baseline"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
params: 
  experiment: experiment 
  baseline: baseline 
  intervention: intervention
  intervention_label: intervention_label
---

@@

```{r read_data, include=False}
experiment <- params$experiment
baseline <- params$baseline
intervention <- params$intervention
intervention_label <- params$intervention_label

out.path <- here::here('output', args$experiment)

base.path <- get_latest_runtime_subdirectory(here::here(out.path, baseline))
int.path <- get_latest_runtime_subdirectory(here::here(out.path, intervention))

base <- read.csv(paste0(base.path, 'qalys.csv'))
int <- read.csv(paste0(int.path, 'qalys.csv'))

combined <- rbind(base, int)
```

@@

```{r}
QALY_comparison(base = base,
                base.name = baseline,
                int = int,
                int.name = intervention)
```

@@

```{r}
sf12.plots(base = base,
           base.name = baseline,
           int = int,
           int.name = intervention)
```

@@

```{r}
auc.plots(base = base,
          base.name = baseline,
          int = int,
          int.name = intervention)
```

@@

```{r}
cost.per.qaly(base = base,
              base.name = baseline,
              int = int,
              int.name = intervention,
              QALY_value = 60000,  # QALY value == £60,000
              int.label <- intervention_label)
```

@@

```{r}
ICER(base = base,
     base.name = baseline,
     int = int,
     int.name = intervention,
     QALY_value = 60000,
     int.label = intervention_label)
```

@@

```{r}
intervention.cost(base = base,
                  base.name = baseline,
                  int = int,
                  int.name = intervention,
                  int.label = intervention_label)
```
